---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- output: rmarkdown::github_document -->
<!-- output: html_notebook -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# gdalR package

This is a repo for package that contains a collection of functions that call GDAL externally on the [milkun cluster](http://wiki.science.ru.nl/cncz/Hardware_servers?setlang=en#.5BReken-.5D.5BCompute_.5Dservers.2Fclusters).

To install the package, run:
```{r install, eval = FALSE}
devtools::install_github("mirzacengic/gdalR")
```


**NOTE:** Functions are not that general. They're designed to work on milkun cluster (Linux), but can be adapted to be more generalized. Requires GDAL installed.
## Working list of functions utilized right now
- GDAL_LC_tile() - split, process, and merge rasters in parallel.  
- GDAL_algebra() - raster algebra.  
- GDAL_aspect() - calculate aspect from DEM.  
- GDAL_crop() - crop raster with shapefile. *Only this function has some documentation.*  
- GDAL_mosaic_tile() - lower level function that merges back tiled raster from GDAL_LC_tile.  
- GDAL_reproject() - reproject raster.  
- GDAL_resample() - resample raster.  
- GDAL_slope() - calculate slope from DEM.  
- GDAL_get_changes() - extract changes from two raster from different timesteps with gdal_calc.py. **Needs debugging!**  
- GDAL_raster_to_polygon() - convert raster to a polygon (ESRI Shapefile) using gdal_polygonize.py.  
